Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Below

We now evaluate our algorithm and show that it is effective in practice, even on the larger subgraph
isomorphism instances. In the first two plots of \cref{figure:runtimes} we give cumulative
distributions for the induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we
discuss the dotted lines in this plot below). The results are strong: with $k = 0$ we may solve
nearly every instance, whilst even at $k = 5$ we can solve over $4,000$ instances in both variants.

@@

\subsection{Solving from the Top Down}

>>>>

We now evaluate our algorithm and show that it is effective in practice, even on the larger subgraph
isomorphism instances. In the first two plots of \cref{figure:runtimes} we give cumulative
distributions for the induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we discuss
the dotted lines in this plot in \cref{section:topdown}). The results are strong: with $k = 0$ we
may solve nearly every instance, whilst even at $k = 5$ we can solve over $4,000$ instances in both
variants.

@@

\subsection{Solving from the Top Down}\label{section:topdown}
